---
title: 'Survey Data: Properly Prepping, Analyzing, and Modeling For Research'
author: "Lindsay Warrell & Jonathan Zhang"
date: "`r Sys.Date()`"
output: html_document
---

## **Mixed Effects Modeling**

## Objectives

| In this module, we will learn:
| 1. How to clean and manipulate survey data.
| 2. How to calculate descriptive statistics using survey data
| 3. How to determine what type of analyses on survey data.

## **BUT FIRST:**

## **Why Use Survey Data in Anthropology?**

Survey data helps anthropologists:

1.  Understand cultural trends and social behavior.

2.  Collect both quantitative and qualitative data, providing different approaches that analyzing both broad trends and detailed insights within R.

3.  Compare societies/populations across different worlds and time periods.

4.  Quantify ethnographic findings with statistical evidence.

**Example:**

------------------------------------------------------------------------

## **1. Loading and Exploring Data**

We will use a `survey` dataset for this Module. We will need to install some packages needed to run the code and explore it:

```{r}
# First install these packages
library(tidyverse)
library(curl)
```

```{r}
# Load the dataset
```
