---
title: 'Survey Data: Properly Prepping, Analyzing, and Modeling For Research'
author: "Lindsay Warrell & Jonathan Zhang"
date: "`r Sys.Date()`"
output: html_document
---

## **Mixed Effects Modeling**

## Objectives

| In this module, we will learn:
| 1. How to clean and manipulate survey data.
| 2. How to calculate descriptive statistics using survey data
| 3. How to determine what type of analyses on survey data.

## **BUT FIRST:**

## **Why Use Survey Data in Anthropology?**

Survey data helps anthropologists:

1.  Understand cultural trends and social behavior.

2.  Collect both quantitative and qualitative data, providing different approaches that analyzing both broad trends and detailed insights within R.

3.  Compare societies/populations across different worlds and time periods.

4.  Quantify ethnographic findings with statistical evidence.

**Example:**

------------------------------------------------------------------------

## **1. Loading and Exploring Data**

We will use a `survey` dataset for this Module. We will need to install some packages needed to run the code and explore it:

```{r}
# First install these packages
library(tidyverse)
library(curl)
```

```{r}
# Load the dataset
C<-curl("https://raw.githubusercontent.com/ZeddyCraft/AN588-Group-Presentation/refs/heads/main/Cleaned%20Data%20(Updated).csv")
Survey<-read.csv(C)
```

##Qualitative Statistics

One of the most useful parts of surveys is qualitative statistics or data represented by words or phrases, not numbers. Take for example, the "BU_Description" column, based on the prompt "Describe BU in one word". 

```{r}
head(Survey$BU_Description)
```
Even in the first few words, we have a large variety of responses! But how can we organize this data? How can we analyze it? Traditional methods of data visualization don't work and neither do traditional methods of analysis. One way of data visualization is through word clouds.
Word clouds correlate the frequency of a descriptor with the size of the word in the image, giving us a visual representation of these descriptions. 

```{r}
library(wordcloud2)
wordcloud2(Survey$BU_Description, color="random-light", backgroundColor="grey")
```