<<<<<<< HEAD
---
title: 'Survey Data: Properly Prepping, Analyzing, and Modeling For Research'
author: "Lindsay Warrell & Jonathan Zhang"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# **Using Survey Data in Anthropology: Properly Prepping, Analyzing, and Modeling**

## Preliminaries

This module introduces how survey data can be a powerful tool in
anthropological research by using real-world responses from a survey
done in this class. Surveys allow anthropologists to gather insights
into cultural beliefs, behaviors, and perceptions across diverse
populations. In this module, you'll explore how structured survey
responses can be analyzed to reveal patterns and meanings relevant to
social science questions. To get started, you’ll need the following:

**Required packages**

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(curl)
library(ggplot2)
library(tm)
library(wordcloud)
library(RColorBrewer)
```

## Objectives

| In this module, we will learn:
| 1. How to clean and manipulate survey data.
| 2. How to calculate descriptive statistics using survey data
| 3. How to determine what type of analyses we can do with survey data.

**BUT FIRST:**

**Why Use Survey Data in Anthropology?**

Survey data helps anthropologists:

1.  Understand cultural trends and social behavior.

2.  Collect both quantitative and qualitative data, providing different
    approaches that analyzing both broad trends and detailed insights
    within R.

3.  Compare societies/populations across different worlds and time
    periods.

4.  Quantify ethnographic findings with statistical evidence.

**Example:** Imagine a cultural anthropologist studying youth
perceptions of education across rural and urban communities in Kenya.
Through open-and closed-ended survey questions, they can:

-   Quantitatively measure how many respondents believe education leads
    to job security.

-   Qualitatively analyze why they hold those beliefs based on open-text
    responses.

-   Use R to visualize group differences (e.g., urban vs. rural) and run
    regression models to predict educational outlook based on
    socioeconomic variables.

**1. Loading and Exploring the Data**

We will use a `survey` dataset for this Module. We will need to install
some packages needed to run the code and explore it:

```{r}
# Load the raw dataset
raw_data <- curl("https://github.com/ZeddyCraft/AN588-Group-Presentation/raw/refs/heads/main/AN588%20Survey%20(Responses)%20-%20Form%20Responses%201.csv")
d <- read.csv(raw_data, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

# Challenge 1: Reviewing Survey Data

Take a moment to explore the raw survey data above. Before we begin
analysis, consider the following questions:

1.  What is wrong with this dataset here?

2.  What will likely happen if we run an analysis with right now?

3.  What challenges or limitations would this impose on our research?

*Why Cleaning Your Data Matters*

Before conducting any kind of analysis, it’s essential to clean your
data. Dirty or inconsistent data can lead to misleading results or
errors in your analysis. Common cleaning steps include:

-   Renaming or relabeling columns for clarity
-   Converting text responses to numeric or categorical variables (e.g.
    as.numeric)
-   Handling missing data appropriately
-   Standardizing scales (e.g., Likert items)

You can clean your data using R (e.g., `mutate()`, `rename()`,
`filter()` functions in `dplyr`), or manually in a spreadsheet if the
dataset is small. The cleaned version used in this module is already
processed for demonstration.

Now load this cleaned dataset:

```{r}
# Load the dataset
cleaned_data <- curl("https://github.com/ZeddyCraft/AN588-Group-Presentation/raw/refs/heads/main/Cleaned_Data.csv")
d <- read.csv(cleaned_data, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

Discussion: What differences do you see with this dataset? How does it
influence our research going forward?

*TAKEAWAY: Clean you data!!*

# Challenge 2: Test a Hypothesis

**Topic:** Regression Modeling in Survey Research

**Objective:** Use basic regression models to compare the predictive power of confidence and anxiety on job security.

```{r challenge-hypothesis}
survey_data <- d
Confidence <- d$Academic_Confidence
Anxiety <- d$Future_Anxious
JobSecurity <- d$Job_Confidence
```

```{r}
# Two regression models
model_conf <- lm(JobSecurity ~ Confidence, data = survey_data)
model_anx <- lm(JobSecurity ~ Anxiety, data = survey_data)

summary(model_conf)
summary(model_anx)
```

```{r}
# Compare R-squared values
conf_r2 <- summary(model_conf)$r.squared
anx_r2 <- summary(model_anx)$r.squared

bar_data <- tibble(
  Predictor = c("Academic Confidence", "Academic Anxiety"),
  R_squared = c(conf_r2, anx_r2)
)
```

**Let's visualize it**
```{r}
# Barplot
ggplot(bar_data, aes(x = Predictor, y = R_squared, fill = Predictor)) +
  geom_col(show.legend = FALSE) +
  ylim(0, 1) +
  labs(
    title = "Prediction of Job Security by Confidence vs. Anxiety",
    y = "R-squared Value",
    x = "Predictor"
  ) +
  theme_minimal()

# Scatterplot
ggplot(d, aes(x = Academic_Confidence, y = Job_Confidence)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Academic Confidence vs. Job Security",
       x = "Academic Confidence",
       y = "Job Security")

# Pearson correlation
jobsecured <- cor.test(d$Academic_Confidence, d$Job_Confidence)
jobsecured
```

**Discussion Prompt:** Which predictor has a stronger relationship with perceived job security? What might this tell us about how confidence and anxiety influence perceptions of the future?

**Takeaway:** Regression helps test relationships between variables — in this case, identifying whether emotional or academic factors are more influential on students' views of their future.

## Qualitative Statistics

One of the most useful parts of surveys is qualitative statistics or
data represented by words or phrases, not numbers. 

Take for example, the "Favorite_Color" column, based on the prompt "What is your favorite
color?".

```{r}
head(d$Favorite_Color)
```

How can we organize this data? How can we analyze it? Traditional
methods of data visualization don't work and neither do traditional
methods of analysis. One way of data visualization is through word
clouds. Word clouds correlate the frequency of a descriptor with the
size of the word in the image, giving us a visual representation of
these descriptions. The package wordcloud2 gives us a function
"wordcloud2" which lets us create these in r.

```{r wordcloud}
library(wordcloud2)
#first let's find the frequency (or counts) of each of the color responses in r
t<-table(d$Favorite_Color)
wordcloud2(t, size=.8, color=(c("Black","Blue","Brown","Cyan","Green","Pink","Purple","Red","Teal","Yellow")))
```

That's visualization! Wordcloud can be an amazing tool to use for your data visuals.

# Challenge 3
Now it's your turn. Let's try making this with the Majors column.

```{r}
t2<-table(d$Major)
wordcloud2(t2, size=.4, color="random-dark")
```

**Discussion Prompt:** What is the most frequent major that appeared in this dataset? Any interesting major in there? 

**Takeaway:** Text data adds depth — a word cloud offers a quick thematic scan, helping anthropologists connect numbers to narratives.

# Conclusion
Survey data is an incredibly flexible tool for anthropologists. In this module, we explored descriptive stats, modeling, and qualitative visualization — all from one simple dataset. The skills here are foundational for both research and applied work.
=======
---
title: 'Survey Data: Properly Prepping, Analyzing, and Modeling For Research'
author: "Lindsay Warrell & Jonathan Zhang"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

## **Survey Data: Properly Prepping, Analyzing, and Modeling For Research**

## Objectives

| In this module, we will learn:
| 1. How to clean and manipulate survey data.
| 2. How to calculate descriptive statistics using survey data
| 3. How to determine what type of analyses we can do with survey data.

## **BUT FIRST:**

## **Why Use Survey Data in Anthropology?**

Survey data helps anthropologists:

1.  Understand cultural trends and social behavior.

2.  Collect both quantitative and qualitative data, providing different
    approaches that analyzing both broad trends and detailed insights
    within R.

3.  Compare societies/populations across different worlds and time
    periods.

4.  Quantify ethnographic findings with statistical evidence.

**Example:** Imagine a cultural anthropologist studying youth
perceptions of education across rural and urban communities in Kenya.
Through open-and closed-ended survey questions, they can:

-   Quantitatively measure how many respondents believe education leads
    to job security.

-   Qualitatively analyze why they hold those beliefs based on open-text
    responses.

-   Use R to visualize group differences (e.g., urban vs. rural) and run
    regression models to predict educational outlook based on
    socioeconomic variables.

## **1. Loading and Exploring Data**

We will use a `survey` dataset for this Module. We will need to install
some packages needed to run the code and explore it:

```{r}
# First install these packages
library(tidyverse)
library(curl)
library(ggplot2)
library(wordcloud)
```

```{r}
# Load the raw dataset
f <- curl("https://raw.githubusercontent.com/ZeddyCraft/AN588-Group-Presentation/refs/heads/main/Cleaned_Survey.csv")
d <- read.csv(f, header = TRUE, sep = ",")
head(d)
```

```{r}
# Describe Your Data
str(d)
summary(d)
```

# Challenge 1: Reviewing Survey Data
Take a moment to explore the raw survey data above. Before we begin analysis, consider the following questions:

1. What is wrong with this dataset here? 

2. How does the wording of the responses influence the responses?

3. What challenges or limitations would this impose on our research?

Now load this dataset:
```{r}
# Load the dataset
f <- curl("https://raw.githubusercontent.com/ZeddyCraft/AN588-Group-Presentation/refs/heads/main/Cleaned_Survey.csv")
d <- read.csv(f, header = TRUE, sep = ",")
head(d)
```

```{r}
# Describe Your Data
str(d)
summary(d)
```

Discussion: What differences do you see with this dataset? How does it influence our research going forward?

IMPORTANT: Clean you data!!


# Challenge 2: Test a Hypothesis

**Hypothesis:** Academic confidence will have a higher prediction rate than anxiousness for perceived job security.

```{r}
survey_data <- d
Confidence <- d$Academic_Confidence
Anxiety <- d$Future_Anxious
JobSecurity <- d$Job_Confidence
```

```{r}
# Two regression models
model_conf <- lm(JobSecurity ~ Confidence, data = survey_data)
model_anx <- lm(JobSecurity ~ Anxiety, data = survey_data)

summary(model_conf)
summary(model_anx)
```

```{r}
conf_r2 <- summary(model_conf)$r.squared
anx_r2 <- summary(model_anx)$r.squared

bar_data <- tibble(
  Predictor = c("Academic Confidence", "Academic Anxiety"),
  R_squared = c(conf_r2, anx_r2)
)

ggplot(bar_data, aes(x = Predictor, y = R_squared, fill = Predictor)) +
  geom_col(show.legend = FALSE) +
  ylim(0, 1) +
  labs(
    title = "Prediction of Job Security by Confidence vs. Anxiety",
    y = "R-squared Value",
    x = "Predictor"
  ) +
  theme_minimal()
```


```{r}
# Scatterplot
ggplot(d, aes(x = Academic_Confidence, y = Job_Confidence)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Academic Confidence vs. Job Security",
       x = "Academic Confidence",
       y = "Job Security")

# Pearson correlation
jobsecured <- cor.test(d$Academic_Confidence, d$Job_Confidence)
jobsecured
```

```{r}
dummy <- fastDummies::dummy_cols(d)
dummy
```

```{r}
fastDummies_example <- data.frame(numbers = 0:50,
                    age = c(d$Age),
                    gender  = c(d$Gender),
                    height = c(d$Height.In.),
                    weight   = c(d$Weight.lbs),
                    stringsAsFactors = FALSE)
knitr::kable(fastDummies_example)
```

\`\`\`{r} model \<- lm(Gender \~ Age + height + weight,
data=survey_demo)

Outline for analysis:

\- Cross-comparasion (Males vs Females vs Non-Binary)

\- Correlations Analysis

 - inferential statistics

 - Word Cloud Analysis (qualitive data):

Lindsay - Descriptive Statistic (quantatitive data): Jon - regression
analysis?:

Jon - college student's anxious to predicting likihood to secure job?

Cite some references for analyzing survey data
>>>>>>> e8c759f62a3c9d99be16c6ac56bfbc019e5cfdba
